Twisted \(M\)-theory and its perturbative quantization.

### 2021-02-12 paper.tex
merge

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}

@@

Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.

\begin{lem}
  Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the $Q$-cohomology of $\m2$.
  There is an isomorphism of $\ZZ/2$-graded Lie algebras
  \[
    \m2^Q \simeq \fsl(5;\CC) \ltimes ???
  \]
\end{lem}

@@

When $X$ is Calabi--Yau of complex dimension $n$, the holomorphic volume form $\Omega$ defines an isomorphism
\[
  \vdash \Omega : \pv^{i,j}(X) \cong \Omega^{n-i, j}(X).
\]
In turn, the holomorphic de Rham operator $\partial : \Omega^{p, j}(X) \to \Omega^{p+1,j}$ defines a holomorphic differential operator
\[
  \partial_{\Omega} : \pv^{i,j}(X) \to \pv^{i-1,j}(X) .
\]
This is the holomorphic analog of the divergence operator with respect to $\Omega$.

>>>>

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}

@@

Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
Fix a rank one supercharge $Q \in S \subset \ft_{11d}$ satisfying $Q^2 = 0$. 
We will characterize the cohomology of the algebra $\m2$ with respect to this supercharge. 
Before doing this, let us set up some notation.

Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
As $\fsl(L ; \CC) = \fsl(5 ; \CC)$-modules the supersymmetry algebra decomposes as
\[
L \oplus L^* \oplus \CC_t
\]
and $\so(11, \CC)$ decomposes as
\[
\wedge^2 L \oplus \wedge^2 L^* \oplus L \oplus L^* .
\]
Furthermore, the spinorial representation can be identified with
\[
S = \wedge^\bu (L^*) = \CC \oplus L^* \oplus \wedge^2 L^* \oplus \wedge^3 L^* \oplus \wedge^4 L^* \oplus \wedge^5 L^* .
\]
The element $Q$ lives in the first summand.

\begin{lem}
Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the $Q$-cohomology of $\m2$.
There is an isomorphism of $\ZZ/2$-graded Lie algebras
  \[
    \m2^Q \simeq \fsl(5;\CC) \ltimes \Pi (\wedge^2 L^* \oplus \CC\cdot c)
  \]
\end{lem}
\begin{proof}
According to the $\ZZ \times \ZZ/2$ bigrading, $Q$ is degree $(0,{\rm odd})$.
Since the differential on $\m2$ is degree $(1,{\rm even})$, the total cohomology with respect to $\d + [Q,-]$ will only be $\ZZ/2$ graded.

We spell out the action of $[Q,-]$ on $S$ according to the above decompositions.
First, note that
\[
[Q,-] \colon S \to L^* \oplus \CC_t
\]
is surjective and has $26$-dimensional kernel. 
\end{proof}

@@

When $X$ is Calabi--Yau of complex dimension $n$, the holomorphic volume form $\Omega$ defines an isomorphism
\[
  \vee \Omega : \pv^{i,j}(X) \cong \Omega^{n-i, j}(X).
\]
In turn, the holomorphic de Rham operator $\partial : \Omega^{p, j}(X) \to \Omega^{p+1,j}$ defines a holomorphic differential operator
\[
  \partial_{\Omega} : \pv^{i,j}(X) \to \pv^{i-1,j}(X) .
\]
This is the holomorphic analog of the divergence operator with respect to $\Omega$.
